Understanding the Black-box Structure of Epidemiology Simulators\\ for Policy Decision Making

### 2019-04-25 paper/icml_ai4good/main.tex
sort out table

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{graphicx}
% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
  \begin{table*}[h!]
  \footnotesize
  \setlength{\tabcolsep}{1mm}
  \caption{Addresses }
  \label{table:addresses}
  \def\arraystretch{1.25}
  % \setlength{\tabcolsep}{1mm}
  \begin{tabularx}{\textwidth}{@{}lX@{}} 
    \toprule
    Address ID & Full address \\
    \midrule
  A1 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const)+0x28a;

  OM::Population::createInitialHumans()+0x94;

  OM::Population::newHuman(OM::SimTime)+0x5c;

@@

  OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\
  % A2 & [forward()+0x204; 
  % OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

  %  OM::Population::update1(OM::SimTime)+0x1e9;

  %  OM::Population::newHuman(OM::SimTime)+0x5c;

  %  OM::Host::Human::Human(OM::SimTime)+0x12b;

  %  OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99;

  %  OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a;

  %  OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6;

  %  OM::util::random::gauss(double, double)+0xb4]\_\_Normal \\
  % A3 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

  %  OM::Host::Human::update(bool)+0x22c;

  %  OM::Host::InfectionIncidenceModel::numNewInfections(OM::Host::Human const\&, double)+0x2a3;

  %  OM::util::random::poisson(double)+0x13f]\_\_Poisson\\
  % A4 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

  %  OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96;

  %  OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9;

    % OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
    $\vdots$ & $\vdots$ \\
%   A5 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

%     OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96;

%     OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9;

%     OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
%   A6 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

@@

%   OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
A11 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc;

OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8;

OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xad;

OM::Clinical::CM5DayCommon::severeMalaria(OM::Host::Human\&, OM::Clinical::Episode::State, double, int\&)+0x4b1;
OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
\bottomrule
  \end{tabularx}
  \end{table*}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{graphicx}
% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
  \begin{table*}[h!]
  \footnotesize
  \setlength{\tabcolsep}{1mm}
  \caption{Addresses }
  \label{table:addresses}
  \def\arraystretch{1.25}
  % \setlength{\tabcolsep}{1mm}
  \begin{tabularx}{\textwidth}{@{}lX@{}} 
    \toprule
    Address ID & Full address \\
    \midrule
  A1 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const)+0x28a;
  OM::Population::createInitialHumans()+0x94;
  OM::Population::newHuman(OM::SimTime)+0x5c;

@@

  OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\

   $\vdots$ & $\vdots$ \\
  A5 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

   OM::Population::update1(OM::SimTime)+0xff;

    OM::Host::Human::update(bool)+0x2bc;

    OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96;

    OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9;

    OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\

%   A6 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

@@

%   OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
 $\vdots$ & $\vdots$ \\

% A11 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468;

% OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xad;

% OM::Clinical::CM5DayCommon::severeMalaria(OM::Host::Human\&, OM::Clinical::Episode::State, double, int\&)+0x4b1;

% OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\

\bottomrule
  \end{tabularx}
  \end{table*}
